Step 1: Installing Packages

```{r eval=FALSE, include=TRUE}
install.packages("quantmod")
library(quantmod)
install.packages("devtools")
devtools::install_github("nipfpmf/eventstudies", ref="master")
library(dplyr)
```

Step 2: Retrieving data using Quantmod for Japanese stocks

```{r eval=FALSE, include=TRUE}
startJP <- as.Date("2018-05-28")
endJP <- as.Date("2018-07-28")

symbolBasketJP <- c("6113.T", "3865.T", "7211.T", "9735.T", "3289.T")

getSymbols(symbolBasketJP , src='yahoo', from = startJP, to = endJP)

Amada <- as.xts(`6113.T`)
names(Amada) <- c("Amada.Open"   ,  "Amada.High"   ,  "Amada.Low"   ,   "Amada.Close"  , "Amada.Volume",  "Amada.Adjusted")

Hokuetsu <- as.xts(`3865.T`)
names(Hokuetsu) <- c("Hokuetsu.Open"   ,  "Hokuetsu.High"   ,  "Hokuetsu.Low"   ,   "Hokuetsu.Close"  ,  "Hokuetsu.Volume",  "Hokuetsu.Adjusted")

Mitsubishi <- as.xts(`7211.T`)
names(Mitsubishi) <- c("Mitsubishi.Open"   ,  "Mitsubishi.High"   ,  "Mitsubishi.Low"   ,   "Mitsubishi.Close"  ,  "Mitsubishi.Volume",  "Mitsubishi.Adjusted")

Secom <- as.xts(`9735.T`)
names(Secom) <- c("Secom.Open"   ,  "Secom.High"   ,  "Secom.Low"   ,   "Secom.Close"  ,  "Secom.Volume",  "Secom.Adjusted")

Tokyu <- as.xts(`3289.T`)
names(Tokyu) <- c("Tokyu.Open"   ,  "Tokyu.High"   ,  "Tokyu.Low"   ,   "Tokyu.Close"  ,  "Tokyu.Volume",  "Tokyu.Adjusted")
```

Step 3: Calculate the daily stock return for the Japanese stocks

```{r eval=FALSE, include=TRUE}
Amada_Close <- Amada[, "Amada.Close", drop = FALSE]
Amada_Return <- (diff(Amada_Close)/Amada_Close[-length(Amada_Close)])*100
names(Amada_Return) <- c("Amada")
  
Hokuetsu_Close <- Hokuetsu[, "Hokuetsu.Close", drop = FALSE]
Hokuetsu_Return <- (diff(Hokuetsu_Close)/Hokuetsu_Close[-length(Hokuetsu_Close)])*100
names(Hokuetsu_Return) <- c("Hokuetsun")

Mitsubishi_Close <- Mitsubishi[, "Mitsubishi.Close", drop = FALSE]
Mitsubishi_Return <- (diff(Mitsubishi_Close)/Mitsubishi_Close[-length(Mitsubishi_Close)])*100
names(Mitsubishi_Return) <- c("Mitsubishi")

Secom_Close <- Secom[, "Secom.Close", drop = FALSE]
Secom_Return <- (diff(Secom_Close)/Secom_Close[-length(Secom_Close)])*100
names(Secom_Return) <- c("Secom")

Tokyu_Close <- Tokyu[, "Tokyu.Close", drop = FALSE]
Tokyu_Return <- (diff(Tokyu_Close)/Tokyu_Close[-length(Tokyu_Close)])*100
names(Tokyu_Return) <- c("Tokyu")
```

Step 4: Merging all the stock return datasets

```{r eval=FALSE, include=TRUE}
stockPriceReturnJP<-merge(Amada_Return, Hokuetsu_Return, Mitsubishi_Return, Secom_Return, Tokyu_Return)

View(stockPriceReturnJP)
str(stockPriceReturnJP)
```

Step 5: List the assets and the date of the flood

```{r eval=FALSE, include=TRUE}
eventDateJP<-data.frame("name"=c("Amada","Hokuetsu","Mitsubishi", "Secom", "Tokyu"), "when"=c("2018-06-28","2018-06-28","2018-06-28","2018-06-28","2018-06-28"))
```

Step 6: Convert the text

```{r eval=FALSE, include=TRUE}
eventDateJP$name<-as.character(eventDateJP$name)
eventDateJP$when<-as.Date(eventDateJP$when)
```

Step 7: Event Study analysis for the Japanese stocks

```{r eval=FALSE, include=TRUE}
esJP <- eventstudies::eventstudy(firm.returns = stockPriceReturnJP,
                               event.list = eventDateJP,
                               event.window = 5,
                               type = "None",
                               to.remap = TRUE,
                               remap = "cumsum",
                               inference = TRUE,
                               inference.strategy = "bootstrap",
                               )
```

Step 8: Plot event study

```{r eval=FALSE, include=TRUE}
plot(esJP)
```

Step 9: Japan Flood Results

```{r eval=FALSE, include=TRUE}
class(esJP)
str(esJP)
summary(esJP)
```

Step 10: Retrieving data using Quantmod for India stocks

```{r eval=FALSE, include=TRUE}
startIN <- as.Date("2018-07-16")
endIN <- as.Date("2018-09-16")

symbolBasketIN <- c("TATASTEEL.BO", "TECHM.BO", "BAJAJ-AUTO.BO", "ICICIBANK.BO", "LT.BO")

getSymbols(symbolBasketIN, src='yahoo', from = startIN, to = endIN)

Tata <- as.xts(`TATASTEEL.BO`)
names(Tata) <- c("Tata.Open"   ,  "Tata.High"   ,  "Tata.Low"   ,   "Tata.Close"  ,  "Tata.Volume",  "Tata.Adjusted")

Mahindra <- as.xts(`TECHM.BO`)
names(Mahindra) <- c("Mahindra.Open"   ,  "Mahindra.High"   ,  "Mahindra.Low"   ,   "Mahindra.Close"  ,  "Mahindra.Volume",  "Mahindra.Adjusted")

Bajaj <- as.xts(`BAJAJ-AUTO.BO`)
names(Bajaj) <- c("Bajaj.Open"   ,  "Bajaj.High"   ,  "Bajaj.Low"   ,   "Bajaj.Close"  ,  "Bajaj.Volume",  "Bajaj.Adjusted")

ICICI <- as.xts(`ICICIBANK.BO`)
names(ICICI) <- c("ICICI.Open"   ,  "ICICI.High"   ,  "ICICI.Low"   ,   "ICICI.Close"  ,  "ICICI.Volume",  "ICICI.Adjusted")

LT <- as.xts(`LT.BO`)
names(LT) <- c("LT.Open"   ,  "LT.High"   ,  "LT.Low"   ,   "LT.Close"  ,  "LT.Volume",  "LT.Adjusted")
```

Step 11: Calculate the daily stock return for the Indian stocks

```{r eval=FALSE, include=TRUE}
Tata_Close <- Tata[, "Tata.Close", drop = FALSE]
Tata_Return <- (diff(Tata_Close)/Tata_Close[-length(Tata_Close)])*100
names(Tata_Return) <- c("Tata")
  
Mahindra_Close <- Mahindra[, "Mahindra.Close", drop = FALSE]
Mahindra_Return <- (diff(Mahindra_Close)/Mahindra_Close[-length(Mahindra_Close)])*100
names(Mahindra_Return) <- c("Mahindran")

Bajaj_Close <- Bajaj[, "Bajaj.Close", drop = FALSE]
Bajaj_Return <- (diff(Bajaj_Close)/Bajaj_Close[-length(Bajaj_Close)])*100
names(Bajaj_Return) <- c("Bajaj")

ICICI_Close <- ICICI[, "ICICI.Close", drop = FALSE]
ICICI_Return <- (diff(ICICI_Close)/ICICI_Close[-length(ICICI_Close)])*100
names(ICICI_Return) <- c("ICICI")

LT_Close <- LT[, "LT.Close", drop = FALSE]
LT_Return <- (diff(LT_Close)/LT_Close[-length(LT_Close)])*100
names(LT_Return) <- c("LT")
```

Step 12: Merging all the stock return datasets

```{r eval=FALSE, include=TRUE}
stockPriceReturnIN<-merge(Tata_Return, Mahindra_Return, Bajaj_Return, ICICI_Return, LT_Return)

View(stockPriceReturnIN)
str(stockPriceReturnIN)
```

Step 13: List the assets and the date of the flood

```{r eval=FALSE, include=TRUE}
eventDateIN<-data.frame("name"=c("Tata","Mahindra","Bajaj", "ICICI", "LT"), "when"=c("2018-08-16","2018-08-16","2018-08-16","2018-08-16","2018-08-16"))
```

Step 14: Convert the text

```{r eval=FALSE, include=TRUE}
eventDateIN$name<-as.character(eventDateIN$name)
eventDateIN$when<-as.Date(eventDateIN$when)
```

Step 15: Event Study analysis for the Indian stocks

```{r eval=FALSE, include=TRUE}
esIN <- eventstudies::eventstudy(firm.returns = stockPriceReturnIN,
                               event.list = eventDateIN,
                               event.window = 5,
                               type = "None",
                               to.remap = TRUE,
                               remap = "cumsum",
                               inference = TRUE,
                               inference.strategy = "bootstrap",
                               )
```

Step 16: Plot event study

```{r eval=FALSE, include=TRUE}
plot(esIN)
```

Step 17: India Flood Results

```{r eval=FALSE, include=TRUE}
class(esIN)
str(esIN)
summary(esIN)
```

Step 18: Market Data for Japan
```{r eval=FALSE, include=TRUE}
JPMKT <- read.csv("JP MKT.csv")

JPMKT$Return <- ((JPMKT$Close-JPMKT$Open)/JPMKT$Open)*100

marketReturnJP<-JPMKT[,c(1, 8)]
marketReturnJP <- read.zoo(marketReturnJP, drop=FALSE)
View(marketReturnJP)
str(marketReturnJP)
```

Step 19: Market Model for Japan floods

Step 20: Plot Market Model for Japan floods

Step 21: Results for Market Model for Japan floods